---
title: "Asignment 3: GGplot"
author: "Adler Torres"
date: "`r format(Sys.time(), '%Y-%b-%d, %I:%M %p')`"
output: html_document
---

## Package Preparation
```{r}
library(ggplot2)
data("trees")
head(trees)
```

### Question 1
#### Create a histogram showing distribution of Girth
```{r message = FALSE}
summary(trees)
girth.histogram <- ggplot(data = trees,
                          aes(x = Girth)) +
  geom_histogram(fill = "pink") +
  labs(title = "Histogram of Tree Girth",
    x = "Girth of Trees",
       y = "Count") +
  theme(
    plot.title = element_text(size = 18, face = "bold", hjust = 0.5),
    axis.title.x = element_text(size = 14, face = "bold"),
    axis.title.y = element_text(size = 14, face = "bold"),
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12)
  )
girth.histogram
```

### Question 2
#### Create a histogram showing the distribution of Volume.
```{r message = F}
volume.histogram <- ggplot(data = trees,
                           aes(x = Volume)) +
  geom_histogram(fill = "orange") +
  labs(title = "Histogram of Tree Volume",
    x = "Volume of Trees",
       y = "Count") +
  theme(
    plot.title = element_text(size = 18, face = "bold", hjust = 0.5),
    axis.title.x = element_text(size = 14, face = "bold"),
    axis.title.y = element_text(size = 14, face = "bold"),
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12)
  )
volume.histogram
```

### Question 3 
#### Create a scatterplot showing the relationship between Girth and Volume
```{r message = FALSE}
trees.scatterplot <- ggplot(data = trees,
                            aes(Girth, Volume)) +
  geom_point(colour = "red") +
  labs(title = "Relationship between Girth and Volume",
    x = "Girth",
       y = "Volume") +
  theme(
    plot.title = element_text(size = 18, face = "bold", hjust = 0.5),
    axis.title.x = element_text(size = 14, face = "bold"),
    axis.title.y = element_text(size = 14, face = "bold"),
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12)
  )
trees.scatterplot
```

### Question 4
#### Use the Shapiro–Wilk test to assess whether Volume is normally distributed. Report the p-value and state whether the data are normally distributed.
```{r warning = FALSE}
Volume.aov <- aov(Volume ~ Volume, data = trees)
```
```{r}
summary.aov(Volume.aov)
```
```{r}
Volume.resid <- residuals(Volume.aov)
shapiro.test(Volume.resid)
```
Thanks to the p-value resulting from this test being under 0.05, with a score of 0.003579, we can conclude that the data is NOT normally distributed thanks to there being signficant difference between data in this category. <br>
<br>
<br>

### Question 5
####  Repeat the Shapiro–Wilk test for Girth. Report the p-value and state whether Girth is normally distributed.
```{r warning = FALSE}
Girth.aov <- aov(Girth ~ Girth, data = trees)
```
```{r}
summary.aov(Girth.aov)
```
```{r}
Girth.resid <- residuals(Girth.aov)
shapiro.test(Girth.resid)
```
Despite Volume showcasing a clear difference between data thanks to a low p-value, the Shapiro-Wilk test reveals that values pertaining to the category of Girth are normally distributed, thanks to a p-value over 0.05, that of which being 0.08893.